---
title: "Reading pixelated values"
author: "Heike Hofmann"
date: "2/6/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r message = FALSE}
library(tidyverse)
pixels <- readxl::read_excel("pixel-measurements.xlsx")
glimpse(pixels)
# write.csv(pixels, file="Data/pixel-values.csv", row.names=FALSE)
```
The `pixels` data set consists of the following set of variables:

- `State` is the name of the state or territory measured.
- `Unaccounted` is the width/height of the grey band on the outside of each square. each square is 541 x 541 pixels. The area of the grey band (?) corresponds to the percentage of persons not accounted for in each state.
- `Agriculture` is the width in pixels of the left most bar in each state. The following two columns, `Male` and `Female` are the height in pixels of the two rectangles making up the left most strip.
- the next sets of three variables are organized in the same way, i.e. `Trade` is the width of the second most left band, `Female` and `Male` are the heights of the rectangles within that strip.
- The `Control.number` is based on the sum of the widths minus the average of the sums from the `Female` and `Male` columns.

Just to get an idea of the size of the unaccounted population, we have:

```{r}
summary((541^2 - (541-2*pixels$Unaccounted)^2)/541^2)
```


In a next step, we want to compare these numbers to the data from the Census Bureau's state aggregates.
```{r}
empl <- read.csv("Data/employment.csv")
```

Extract variables concerned with manufacturing. The denominator in our calculation is not right - we are using total population. However, the comparison on the chart used is population over the age of 10. 
```{r}
manufacturing <- empl %>% select(
  State, TOTAL.POPULATION,
  TOTAL.HANDS.EMPLOYED.IN.MANUFACTURING,
  MALES.ABOVE.AGE.16.EMPLOYED.IN.MANUFACTURING,
  FEMALES.ABOVE.AGE.16.EMPLOYED.IN.MANUFACTURING,
  YOUTHS.EMPLOYED.IN.MANUFACTURING) 
manufacturing <- manufacturing %>% mutate(
  manuPerc = TOTAL.HANDS.EMPLOYED.IN.MANUFACTURING/TOTAL.POPULATION*100,
  menPerc = MALES.ABOVE.AGE.16.EMPLOYED.IN.MANUFACTURING/TOTAL.HANDS.EMPLOYED.IN.MANUFACTURING * 100,
  womenPerc = FEMALES.ABOVE.AGE.16.EMPLOYED.IN.MANUFACTURING/TOTAL.HANDS.EMPLOYED.IN.MANUFACTURING * 100,
  youthsPerc = YOUTHS.EMPLOYED.IN.MANUFACTURING/TOTAL.HANDS.EMPLOYED.IN.MANUFACTURING * 100
)
```

Create comparable variables from pixel side:
```{r}
manu_pixel <- pixels %>% select(State, Manufacturing, Mfctr.Male, Mfctr.Female) %>% mutate(
  State=toupper(State),
  manuPercPix = Manufacturing/451*100,
  menPercPix = Mfctr.Male/(Mfctr.Male+Mfctr.Female)*100,
  womenPercPix = Mfctr.Female/(Mfctr.Male+Mfctr.Female)*100
)
  
```
Combine the two datasets:


```{r}
combo <- left_join(manu_pixel, manufacturing, by="State")
combo %>% ggplot(aes(x = manuPercPix, y = manuPerc)) + 
  geom_abline(colour = "grey50") +
  geom_smooth(method="lm", se=FALSE) + geom_point() +
  ggrepel::geom_label_repel(aes(label=State), combo %>% filter(manuPercPix >= 15))
```

Comparing the percentages for men and women (and youths in manufacturing). The error bars are based on %men at the lower end and %men and %youths at the upper end. The percentage of men employed in manufacturing based on the pixelated value should fall within that. 

```{r}
combo %>% mutate(State = reorder(State, menPerc)) %>%
  ggplot(aes(x = menPercPix, y = State)) +
  geom_errorbarh(aes(xmin=menPerc, xmax=menPerc+youthsPerc)) +
  geom_point()
```

```{r}
occupation <- read.csv("Data/occupation.csv")
occupation$State <- as.character(occupation$Area.name)
occupation$employed <- rowSums(occupation[,-c(1,12:13)])
pixels2 <- pixels %>% mutate(
  employed = Agriculture+Manufacturing+Trade+Services+School
)

combo2 <- left_join(pixels2, occupation, by="State")
combo2 %>% 
  ggplot(aes(x = Agriculture/employed.x, y = (Agriculture.Female+Agriculture.Male)/employed.y)) +
  geom_point()
combo2 %>% 
  ggplot(aes(x = Manufacturing/employed.x, y = (Manufacturing.Female+Manufacturing.Male)/employed.y)) +
  geom_point()
combo2 %>% 
  ggplot(aes(x = Trade/employed.x, y = (Trade.Female.y+Trade.Male.y)/employed.y)) +
  geom_point()
combo2 %>% 
  ggplot(aes(x = Services/employed.x, y = (Service.Female+Service.Male)/employed.y)) +
  geom_point()
combo2 %>% 
  ggplot(aes(x = School/employed.x, y = (School.Female+School.Male)/employed.y)) +
  geom_point()

```

Looks like we found the right data! 

# Reshaping the data

```{r, fig.height=16, fig.width=10}
occ2 <- occupation %>% gather(key="Occupation.Gender", value="Number", 2:11, factor_key = TRUE)
occ2 <- occ2 %>%  
  separate(Occupation.Gender, into=c("Occupation", "Gender"))

occ2 <- occ2 %>% mutate(
  Occupation = factor(Occupation, levels=c("Agriculture", "Manufacturing", "Trade", "Service", "School")),
  Gender = factor(Gender, levels=c("Male", "Female"))
)

cols <- c("#666633", "#264073", "#ffcc00", "#7587bd", "#ffe680")
occ2 %>% 
  ggplot(aes(x=1, weight=Number)) + 
  geom_bar(position="fill", aes(fill=Occupation)) + coord_flip() +
  facet_wrap(~Area.name, scales="free", ncol=6) + ylab("") + xlab("") +
  theme(legend.position="top") +
  scale_fill_manual(values = cols) +
  scale_y_reverse() +
  theme(axis.line=element_blank(), axis.text.y=element_blank(), 
        axis.title = element_blank(), axis.ticks.y = element_blank())
```


```{r, fig.height=5, fig.width=5}

cols <- c("#666633", "#264073", "#ffcc00", "#7587bd", "#ffe680")

library(ggmosaic)
occ2 %>% ggplot() +
  geom_mosaic(aes(x = product(Gender, Occupation), 
                  fill=Occupation, alpha = Gender, weight = Number),
              offset = 0.005) + 
  scale_fill_manual(values=cols) + theme_bw() +
  scale_alpha_manual(values=c(0.8,1))
```
```{r, fig.height=16, fig.width=10}
occ2 %>% ggplot() +
  geom_mosaic(aes(x = product(Gender, Occupation), 
                  fill=Occupation, weight = Number, alpha=Gender)) + 
  theme_bw() +
  facet_wrap(~State, scales="free", ncol=6) + 
  theme(legend.position="top") +
  scale_fill_manual(values = cols) +
  scale_alpha_manual(values=c(0.8,1)) +
  theme(axis.line=element_blank(), axis.text=element_blank(), 
        axis.title = element_blank(), axis.ticks = element_blank())
```
